Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach

### 2021-04-13 0_manuscript_blind/itt-emotion_blind_V7-2.tex
V7-2 after showing to Nonaka again, preparing all files, cover letter still to be written yet

  We analyzed expectations and satisfaction factors in Chinese and Western cultures, comparing soft attributes, such as service, with hard attributes, such as location and facilities, and studied different price ranges.
  We collected our data with web crawling, labeled a sample, applied Shannon's entropy to extract these factors, and then used them to classify a more extensive data set with an SVM. We then used dependency parsing and part-of-speech tagging to extract the nouns that were tied to positive adjectives. 
  We found that Chinese tourists are concerned more with room quality than hospitality, whereas, Western tourists are delighted more by the staff behavior. We also found that the lack of a Chinese-friendly environment for Chinese customers and the smell of cigarettes for Western ones can be disappointing factors of their stay. 
  As one of the first studies in the tourism field to use the high-standard Japanese hospitality environment for this analysis, our cross-cultural study contributes to both the theoretical understanding of satisfaction and suggests practical applications and strategies for hotel managers.

@@

  Japan’s hospitality has been known historically to be of the highest quality. \textit{Omotenashi}, which describes the spirit of Japanese hospitality, with roots in Japanese history and tea ceremony, is celebrated worldwide \cite[][]{al2015characteristics}. Consequently, it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor. However, it is known that customers from different countries and cultures have different expectations \cite[][]{engel1990}. Thus, it could be theorized that their satisfaction factors should be different. The Japanese tourist market is gradually becoming diverse because of multicultural tourist populations. This diversity means that the expectations when staying at a hotel will be varied. Therefore, hotel management must cater to these expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.

  Our study focuses on Western and Chinese tourists, considering their numbers. Chinese tourists accounted for 25.63\% of the tourist population. On the other hand, Western countries accounted for 11.4\% of the total, and 7.23\% were countries where English is the official or the de facto national language \cite[][]{jnto2003-2019}. The effect of Chinese tourists on international economies is increasing, along with the number of studies on this phenomenon \cite[][]{sun2017}. Despite this, many tourist-behavior analyses have been performed only involving Western subjects. As such, a knowledge gap existed until recent decades.

  In studies involving Asian populations in the analysis, Chinese-tourist behaviors have been evaluated most commonly \cite[e.g.][]{liu2019, chang2010, dongyang2015}. The few studies reporting comparisons between Asian and Western tourists’ behaviors \cite[e.g.][]{choi2000} are typically survey- or interview-based, using small samples. These studies, although valid, can have limitations, namely, the scale and sampling. In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or traveling with a single purpose. These studies' limited scope often leads to difficulties in observing cultural and language differences in a single study. This creates a need for large-scale cross-cultural studies for the increasing Asian and Western tourist populations. It could be said that Westerners account for a smaller portion of the tourist population compared to Asians. However, according to \cite{choi2000}, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotels. In comparison, their Asian counterparts only spend 25\% of their budget on hotels. Therefore, it is essential to study Asian and Western tourist populations, their differences, and the contrast with the existing literature results. For this, we used a data-driven approach to our analysis.

@@

@@

@@

    However, Japanese hospitality is based on the Japanese culture. Different cultures interacting with it could provide a different evaluation of it. Some might be impressed by it, whereas some might consider other factors more important to their stay in a hotel. This point leads us to a derivative of the aforementioned research question:

@@

    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service. \cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry. It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer. As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction. Previous studies on the dimensions of culture that influence differences in expectations have been performed in the past \cite{donthu1998cultural}. Western and Chinese customers then have very different backgrounds and cultures. These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have. In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer and the order in which they prioritize them.

    However, in this study, we study not overall customer satisfaction but the satisfaction and dissatisfaction that stem from individual-specific expectations, be they conscious or unconscious. For example, if a customer has a conscious expectation of a comfortable bed and a wide shower, and it is realized during their visit, they will be satisfied with this matter. However, suppose that same customer with a conscious expectation of a comfortable bed experienced loud noises at night. In that case, they can be dissatisfied with a different aspect, regardless of the satisfaction towards the bed. Then, the same customer might have packed their toiletries, thinking that the amenities might not include those. They can then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation. This definition of satisfaction does not allow us to examine overall customer satisfaction. However, it will allow us to examine the factors that a hotel can revise individually and how a population perceives them as a whole. In our study, we consider the definitions in \cite{hunt1975} that satisfaction is a realization of an expectation, and we posit that customers can have different expectations towards different service aspects. Therefore, in our study, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service. On the other hand, dissatisfaction is the emotional response to the lack of a realization or under-performance of these conscious or unconscious expectations towards specific service aspects.

    Previous research has also focused more on soft attributes, with little focus on hard attributes, if only focusing on facilities \cite[e.g.][]{shanka2004, choi2001}. However, hard factors, which are uncontrollable by the hotel staff, can play a part in the customers' choice behavior and satisfaction. Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, and the hotel's integration with tours available nearby, among other factors.

    This leads to another couple of research questions:

    \begin{subrsq}
    \begin{rsq}
    \label{rsq:hard_soft}
    To what degree does satisfaction and dissatisfaction stem from hard and soft attributes of the hotel?
    \end{rsq}

>>>>

  Since culture influences expectations, perceptions, and satisfaction, a cross-culture study is necessary to understand the differences between Japan's biggest tourist populations, Chinese and Western tourists. 
  However, with ever-increasing customer populations, this is hard to accomplish without extensive customer base studies. There is a need for an automated method for identifying these expectations at a large scale. For this, we used a data-driven approach to our analysis.
  Our study analyzed their satisfaction factors comparing soft attributes, such as service, with hard attributes, such as location and facilities, and studied different price ranges.
  We collected hotel reviews and extracted keywords to classify the sentiment of sentences with an SVC. We then used dependency parsing and part-of-speech tagging to extract nouns tied to positive adjectives.
  We found that Chinese tourists consider room quality more than hospitality, whereas Westerners are delighted more by staff behavior. Furthermore, the lack of a Chinese-friendly environment for Chinese customers and cigarette smell for Western ones can be disappointing factors of their stay. 
  As one of the first studies in the tourism field to use the high-standard Japanese hospitality environment for this analysis, our cross-cultural study contributes to both the theoretical understanding of satisfaction and suggests practical applications and strategies for hotel managers.

@@

  Japan’s hospitality has been known historically to be of the highest quality. \textit{Omotenashi}, which describes the spirit of Japanese hospitality, with roots in Japanese history and tea ceremony, is celebrated worldwide \cite[][]{al2015characteristics}. Consequently, it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor. However, it is known that customers from different countries and cultures have different expectations \cite[][]{engel1990}. Thus, it could be theorized that their satisfaction factors should be different.

  The Japanese tourist market is gradually becoming diverse because of multicultural tourist populations. This diversity means that the expectations when staying at a hotel will be varied. Cultural backgrounds have a decisive role in aspects of satisfaction and in the perceptions of quality \cite[][]{mattila1999role,winsted1997service}, or behavioral intentions \cite[][]{liu2001relationships}, such as the difference in Westerners and Asians in their willingness to pay more \cite[][]{LEVY2010319}. Since a difference in cultural background can also heavily influence the expectations of customers, as well as their perceptions of quality, the difference between these two can be smaller or larger depending on the culture in reaction to the same service.

  For a growing industry with increasing cultural diversity, it is essential to identify the cross-culture expectations of customers in order to provide the appropriate services, cater to these expectations to ensure and increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.

  In 2017, Chinese tourists accounted for 25.63\% of the tourist population. On the other hand, Western countries accounted for 11.4\% of the total, and 7.23\% were countries where English is the official or the de facto national language \cite[][]{jnto2003-2019}. The effect of Chinese tourists on international economies is increasing, along with the number of studies on this phenomenon, \cite[][]{sun2017}. Despite this, many tourist-behavior analyses have been performed only involving Western subjects. Yet, it is known that Western and Asian customers are heavily differentiated\cite[][]{LEVY2010319}. As such, a knowledge gap existed until recent decades. Considering the numbers of inbound tourists in Japan and our team's language capabilities, our study focuses on Western and Chinese tourists.

  In studies involving Asian populations in the analysis, Chinese-tourist behaviors have been evaluated most commonly \cite[e.g.][]{liu2019, chang2010, dongyang2015}. The few studies reporting comparisons between Asian and Western tourists’ behaviors \cite[e.g.][]{choi2000} are typically survey- or interview-based, using small samples. These studies, although valid, can have limitations, namely, the scale and sampling. In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or traveling with a single purpose. These studies' limited scope often leads to difficulties in observing cultural and language differences in a single study. This creates a need for large-scale cross-cultural studies for the increasing Asian and Western tourist populations. It could be said that Westerners account for a smaller portion of the tourist population compared to Asians. However, according to \cite{choi2000}, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotels. In comparison, their Asian counterparts only spend 25\% of their budget on hotels. Therefore, it is essential to study Asian and Western tourist populations, their differences, and the contrast with the existing literature results.

  However, with ever-increasing customer populations, this is hard to accomplish without extensive studies of the customer base. There is a need for an automated method for identifying these expectations at a large scale. Our study intends to answer the need for such a methodology utilizing machine learning and natural language processing of large amounts of data. For this, we used a data-driven approach to our analysis, taking advantage of hotel review data. With this methodology, we explore the expectations and needs for the two most differing cultures currently interacting with the hospitality industry in Japan.

@@

  With the knowledge that cultural background influences expectations in customers, which is the basis for satisfaction, it becomes important to know the difference in factors influencing satisfaction and dissatisfaction between the most differing and numerous tourist populations in a given area.

@@

  \subsection{Cultural influence in expectation and satisfaction}\label{theory_expectations}

    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service. \cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry. It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer. As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction. It can also be said that satisfaction stems from the perceptions of quality in comparison to these expectations.

    These differences in customers' backgrounds can be summed up in cultural differences as well. In the past, satisfaction and perceived service quality have been found to be influenced by cultural differences \cite[e.g.][]{mattila1999role, winsted1997service}. Service quality perceptions have been studied via measurements such as SERVQUAL \cite[e.g.][]{armstrong1997importance}.

    Previous studies on the dimensions of culture that influence differences in expectations have been performed in the past as well \cite[e.g.][]{MATTILA201910, LEVY2010319, donthu1998cultural}, such as comparing individualism vs. collectivism, high context vs. low context, uncertainty avoidance, among other factors. While culture as a concept is difficult to quantify, some researchers have tried to use these and more dimensions to measure cultural differences, such as the six dimensions described by \cite{hofstede1984culture}, or the nine dimensions of the GLOBE model \cite[][]{house1999cultural}.

    These cultural dimensions are more differentiated in Western and Asian cultures \cite[][]{LEVY2010319}. Our study being located in Japan, it stands to reason that the differences in expectations between Western tourists and Asian tourists should be understood in order to provide a good service. However, even though geographically close, Japanese and Chinese cultures are both very different when it comes to customer service. This is why our study focuses on the difference between Chinese and Western customers in Japan. The contrasting cultural backgrounds between Chinese and Western customers will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have. In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer and the order in which they prioritize them.

    We reviewed the importance of expectations in the development of satisfaction and dissatisfaction and the influence that cultural backgrounds have in shaping these expectations. This is true for overall satisfaction for the service as a whole, as well as individual elements that contribute to satisfaction.

    In this study, we study not overall customer satisfaction but the satisfaction and dissatisfaction that stem from individual-specific expectations, be they conscious or unconscious. For example, if a customer has a conscious expectation of a comfortable bed and a wide shower, and it is realized during their visit, they will be satisfied with this matter. However, suppose that same customer with a conscious expectation of a comfortable bed experienced loud noises at night. In that case, they can be dissatisfied with a different aspect, regardless of the satisfaction towards the bed. Then, the same customer might have packed their toiletries, thinking that the amenities might not include those. They can then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation. This definition of satisfaction does not allow us to examine overall customer satisfaction. However, it will allow us to examine the factors that a hotel can revise individually and how a population perceives them as a whole. In our study, we consider the definitions in \cite{hunt1975} that satisfaction is a realization of an expectation, and we posit that customers can have different expectations towards different service aspects. Therefore, in our study, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service. On the other hand, dissatisfaction is the emotional response to the lack of a realization or under-performance of these conscious or unconscious expectations towards specific service aspects.

@@

    However, Japanese hospitality is based on Japanese culture. Different cultures interacting with it could provide a different evaluation of it. Some might be impressed by it, whereas some might consider other factors more important to their stay in a hotel. This point leads us to a derivative of the aforementioned research question:

@@

  \subsection{Customer expectations beyond service and hospitality}\label{theory_soft_hard}

    Staff behavior, hospitality and service, and therefore \textit{Omotenashi}, are all soft attributes of a hotel. That is, they are non-physical attributes of the hotel, and as such, they are practical to change through changes in management. While it is important to know this, it is not known if the cultural differences between Chinese and Western tourists also influence other expectations and satisfaction factors, such as the hard factors of a hotel.

    Hard factors are attributes uncontrollable by the hotel staff, which can play a part in the customers' choice behavior and satisfaction. Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, and the hotel's integration with tours available nearby, among other factors.

    Besides the facilities, many other aspects of the experience, expectation, and perception of the stay in a hotel can contribute to the overall satisfaction, as well as individual satisfactions and dissatisfactions. However, previous research focuses more on these soft attributes, with little focus on hard attributes, if only focusing on facilities \cite[e.g.][]{shanka2004, choi2001}. Because of this gap in knowledge, we decided to analyze the differences in cultures regarding both soft and hard attributes of a hotel.

    This leads to two of our research questions:

    \begin{subrsq}
    \begin{rsq}
    \label{rsq:hard_soft}
    To what degree do satisfaction and dissatisfaction stem from hard and soft attributes of the hotel?
    \end{rsq}

### 2021-04-13 0_titlepage/itt-emotion-titlepage.tex
V7-2 after showing to Nonaka again, preparing all files, cover letter still to be written yet

        \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
                    % Nagaoka University of Technology, Nagaoka, Japan \\
                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
                    \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
                    % Corresponding Author %  \\
                    % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
                \and
                    \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
                    % Nagaoka University of Technology, Nagaoka, Japan \\
                    \hspace*{1em} \email{mendoza.espana@gmail.com}
                \and
                    \hspace*{1em} Hirofumi Nonaka \at
                    % Nagaoka University of Technology, Nagaoka, Japan \\
                    \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
                \and
                    \hspace*{1em} Toru Hiraoka \at
                    % University of Nagasaki, Nagasaki, Japan \\
                    \hspace*{1em} \email{hiraoka@sun.ac.jp}
                \and
                    \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
                \and
                    \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
        }

>>>>

        \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
                    \hspace*{1em} ORCID: 0000-0002-6437-0866
                \and
                    \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
                    \hspace*{1em} \email{mendoza.espana@gmail.com}
                \and
                    \hspace*{1em} Hirofumi Nonaka \at
                    \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
                \and
                    \hspace*{1em} Toru Hiraoka \at
                    \hspace*{1em} \email{hiraoka@sun.ac.jp}
                \and 
                    \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
                \at 
                    \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
        }
